Methods for Large Scale Learning to Rank

### 2014-10-23 report/Chapters/Background.tex
feedback Sander pagina 20

Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning to Rank method when it is \emph{feature based} and uses \emph{discriminative training}, in which the concepts \emph{feature based} and \emph{discriminative training} are itself defined as:
\begin{description}
\item[Feature Based]{means that all documents under investigation are represented by feature vectors. Those feature vectors reflect the relevance of the documents to the query, or the importance of the document in itself.}
\item[Discriminative Training]{means that the learning process can be well described by the four components of discriminative learning. That is, a Learning to Rank method has its own \emph{input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function}, like the machine learning process described by Figure \ref{fig:discriminative_training}. \emph{Input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function} are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{in order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces.}
	\end{description}
	}
\end{description}

>>>>

Liu \cite{Liu2007} proposes a more narrow definition and only considers ranking methods to be a Learning to Rank method when it is \emph{feature based} and uses \emph{discriminative training}, in which the concepts \emph{feature based} and \emph{discriminative training} are itself defined as:
\begin{description}
\item[Feature Based]{means that all documents under investigation are represented by feature vectors. Those feature vectors reflect the relevance of the documents to the query, or the importance of the document in itself.}
\item[Discriminative Training]{means that the learning process can be well described by the four components of discriminative learning. That is, a Learning to Rank method has its own \emph{input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function}, like the machine learning process described by Figure \ref{fig:discriminative_training}. \emph{Input space}, \emph{output space}, \emph{hypothesis space}, and \emph{loss function} are hereby defined as follows:
	\begin{description}
	\item[Input Space]{contains the objects under investigation. Usually objects are represented by feature vectors, extracted according to different applications.}
	\item[Output Space]{contains the learning target with respect to the input objects.}
	\item[Hypothesis Space]{defines the class of functions mapping the input space to the output space. The functions operate on the feature vectors of the input object, and make predictions according to the format of the output space.}
	\item[Loss Function]{in order to learn the optimal hypothesis, a training set is usually used, which contains a number of objects and their ground truth labels, sampled from the product of the input and output spaces. A loss function calculates the difference between the predictions $\hat{y}$ and the ground truth labels on a given set of data.
	\end{description}
	}
\end{description}
